---
title: "R_ggplot2"
output: html_document
---

# GGPlot graph Format

There is a specificformat to create ggplot graphs

# ggplot (data = <DATA> ) + < GEOM_FUNCTION > (mapping = aes( < MAPPINGS > ))

# geom_functions
# geom_line() , geom_point() , geom_histgram(), 
# geom_col(), geom_bar()
#  geom_boxplot(),  geom_violin(), geom_density()


```{r}

iris

```

```{r}
data = iris
```


# Install ggplot2 if not installed
```{r}
#install.packages("ggplot2")
```

# Load the ggplot2 library
```{r}
library(ggplot2)
```

# Line plot
# describe the trend

```{r}
ggplot(data, aes(1:150, Sepal.Length)) + geom_line()
```

# Scatter plot
# Understand relation between x & y
```{r}
ggplot(data, aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_point()
```

# Bar chart
```{r}
ggplot(data, aes(x = Species, y = Sepal.Length)) +
  geom_col()
```

# Histogram
# Count of each Sepal length occurrence
```{r}
ggplot(data, aes(x = Sepal.Length)) +
  geom_bar()
```

# Histogram
# Count of each Sepal length occurrence
# here can control the groups
```{r}
ggplot(data, aes(Sepal.Length)) +
  geom_histogram(bins = 15)
```

# Density plot
```{r}
ggplot(data, aes(Sepal.Length)) +
  geom_density()
```

# Box plot
```{r}
ggplot(data, aes(x = Sepal.Length)) +  
  geom_boxplot()
```


# Understand distribution of Sepal length for
# different species
```{r}
ggplot(data, aes(x = Species, y = Sepal.Length)) +
  geom_violin()
```


# How to set labels and titles
```{r}

ggplot(data, aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_point() + labs(x='x axis label', y='y axis label',
                      title='title', subtitle='subtitle',
                      caption='image using ggplot2')
```

# Assign the graph to a variable
```{r}
IrisPlot <- ggplot(iris, aes(Sepal.Length, Petal.Length, colour=Species)) + geom_point()
print(IrisPlot)
```


# Modify x, y labels and title

labs() will allows specifying custom x axis and y axis labels

ggtitle() allows to set title for the graph

```{r}
print(IrisPlot + labs(y="Petal length (cm)", x = "Sepal length (cm)") 
   + ggtitle("Petal and sepal length of iris"))
```


# Handling Legends

### Remove the legend

Remove the legend with the help of property “legend.position”

Set it to value “none” and we will not see the legends

```{r}
# Assign basic graph to a variable
graph1 = ggplot(iris, aes(Sepal.Length, Petal.Length, colour=Species)) + geom_point() 
# Remove Legend
graph1 + theme(legend.position="none")
```


### Hide the legend title

```{r}
# Hide the legend title
graph1 + theme(legend.title=element_blank())
```


### Set legend position

```{r}
#Change the legend position
graph1 + theme(legend.position="top")
```

```{r}
graph1 + theme(legend.position="bottom")
```



